---
title: "Central Park Squirrels"
output: 
  html_document
---

This dataset comes from the [2018 Squirrel Census](https://www.thesquirrelcensus.com/about)

## Location plot
The code plots the locations of all squirrel sightings, colored based on their fur color.

```{r, echo=FALSE, include=FALSE}
library(tidyverse)
D = read.csv('2018_Central_Park_Squirrel_Census_-_Squirrel_Data.csv', na.strings = c("", "NA"))
```

```{r, echo=FALSE}
ggplot(data = D) + geom_point(mapping = aes(x = X, y = Y, color = Primary.Fur.Color), alpha=0.3, size=1)
```

## Topic modeling
Some squirrel sightings also include text descriptions. We can use topic modeling to try to identify the different categories of descriptions people include. This code chunk fits a 2-topic model and prints out the words most associated with each topic.
```{r, echo=FALSE, include=FALSE}
library(tm)
library(topicmodels)
```

```{r, echo=FALSE}
corpus <- Corpus(VectorSource(D$Other.Activities %>% na.omit()))
dtm <- DocumentTermMatrix(corpus, control=list(removePunctuation=TRUE))
dtm <- removeSparseTerms(dtm, 0.995)  # Require at least 2/437 descriptions to contain term
dtm <- dtm[apply(dtm , 1, sum) > 0, ]  # Remove descriptions that are now empty
model <- LDA(dtm, k=2, control=list(seed=4))
terms(model,4)
```
